\bf Model Visualization Techniques for a Social Network Model

### 2018-10-03 paper.Rnw
change title, change plots to be grayscale safe, i hate writing conclusions.

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Model Visualization Techniques for a Social Network Model}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Stochastic actor-oriented models (SAOMs), first introduced by Snijders (1996), are a type of statistical network model for dynamic social networks. Unlike other network models, SAOMs are analytically intractable, and therefore hard to interpret. We use model visualization techniques introduced in Wickham et al (2015) better understand these models and their behavior. We use a three-pronged attack: (a) a network visualization to view the \emph{model}, (b) exploring collections of models for parameter interpretation, and (c) delving into the fitting algorithms to gain insight into the underlying mechanisms. With the help of static and dynamic visualizations, we bring the hidden SAOM fitting processes into the foreground, eventually leading to a better understanding and higher accessibility of SAOMs for social network analysts.
\end{abstract}

>>>>

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visualizing Dynamic Social Network Models}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Stochastic actor-oriented models (SAOMs), first introduced by Snijders (1996), are a type of statistical network model for dynamic social networks. Unlike other network models, SAOMs are analytically intractable, and require extensive simulation procedures for model fitting. We use model visualization techniques introduced in Wickham et al (2015) better understand these models and their behavior. We use a three-pronged attack: (a) a network visualization to view the \emph{model}, (b) exploring collections of models for parameter interpretation, and (c) delving into the fitting algorithms to gain insight into the underlying mechanisms. With the help of static and dynamic visualizations, we bring the hidden SAOM fitting processes into the foreground, eventually leading to a better understanding and higher accessibility of SAOMs for social network analysts.
\end{abstract}
